Determining the alternatives for scalar implicature

### 2016-04-26 Paper/Paper.Rmd
new results table and commented out old one

```{r, libraries}
library(dplyr)
library(ggplot2)
library(grid)
library(gridExtra)
library(jsonlite)
library(lme4)
library(lmerTest)
library(knitr)
library(png)
library(rjson)
library(tidyr)
library(xtable)
# library(langcog)
```

@@

```{r xtable, results = "asis"}

# Tuned model run data
plotData <- allModelRunData %>%
  mutate(study = ifelse(numAlts == 5, "Five alts", 
                        ifelse(numAlts == 4, "Four alts",
                               ifelse(numAlts == 3, "Two alts + generic negative ", "Two alts")))) %>%
  gather(Experiment, cors, c(corE6, corE11)) %>%
  mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))

tableCors <- plotData  %>%
  select(cors, study, Experiment, alphas) %>%
  unique() %>%
  mutate(Experiment = ifelse(Experiment == "1b", "Pragmatic_Listener_exp1", "Pragmatic_Listener_exp2")) %>%
  spread(Experiment, cors)

# Plot model performance table
names(tableCors) <- c("Model", "$\\alpha$", "Two alts", "Four alts")
tableCors <- tableCors[c(3, 4, 2, 1),]
tab <- xtable(tableCors, caption = "Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in the two conditions of Experiment 3.")
print(tab, type="latex", floating = TRUE, include.rownames = FALSE, comment = FALSE,
      sanitize.colnames.function = identity)

>>>>

```{r, libraries}
library(rrrsa)
library(dplyr)
library(ggplot2)
library(grid)
library(gridExtra)
library(jsonlite)
library(lme4)
library(lmerTest)
library(knitr)
library(png)
library(rjson)
library(tidyr)
library(xtable)
# library(langcog)
```

@@

```{r xtable, results = "asis"}
check_words <- c("good", "excellent", "liked", "loved", "memorable", "unforgettable", "palatable", "delicious", "some", "all")

exps <- c("e6", "e11")
res_table <- data.frame()
compare_indices2 <- which(peloquinFrank_2Alts$words %in% check_words)
for (exp in exps) {
  two_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_2Alts,
            semanticsVarName = "speaker.p",
            quantityVarName = "stars",
            itemVarName = "words",
            groupName = "scale",
            compareIndices = compare_indices2,
            compareDataName = exp,
            alphas = seq(0, 10, by = 0.1))
  res_table <- rbind(res_table, exp = two_alt_alphas[1, ])
}

compare_indices3 <- which(peloquinFrank_3Alts$words %in% check_words)
for (exp in exps) {
  three_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_3Alts,
              semanticsVarName = "speaker.p",
              quantityVarName = "stars",
              itemVarName = "words",
              groupName = "scale",
              compareIndices = compare_indices3,
              compareDataName = exp,
              alphas = seq(0, 20, by = 0.1))
  res_table <- rbind(res_table, exp = three_alt_alphas[1, ])
}
compare_indices4 <- which(peloquinFrank_4Alts$words %in% check_words)
for (exp in exps) {
  four_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_4Alts,
              semanticsVarName = "speaker.p",
              quantityVarName = "stars",
              itemVarName = "words",
              groupName = "scale",
              compareIndices = compare_indices4,
              compareDataName = exp,
              alphas = seq(0, 10, by = 0.1))
  res_table <- rbind(res_table, exp = four_alt_alphas[1, ])
}
compare_indices5 <- which(peloquinFrank_5Alts$words %in% check_words)
for (exp in exps) {
  five_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_5Alts,
              semanticsVarName = "speaker.p",
              quantityVarName = "stars",
              itemVarName = "words",
              groupName = "scale",
              compareIndices = compare_indices5,
              compareDataName = exp,
              alphas = seq(0, 10, by = 0.1))
  res_table <- rbind(res_table, exp = five_alt_alphas[1, ])
}
res_table$row_num <- seq(1, nrow(res_table))
res_table <- res_table %>% 
  mutate(exp = ifelse(row_num %% 2 == 0, "Human judgments 4-alts", "Human judgments 2-alts"),
         model = ifelse(row_num < 3, "2-alts",
                           ifelse(row_num < 5, "3-alts",
                                  ifelse(row_num < 7, "4-alts", "5-alts"))),
         result = paste0("", round(cor, 2), " (alpha = ", alpha, ")")) %>%
  select(model, result, exp) %>%
  spread(exp, result)

tab <- xtable(res_table[4:1, ], caption = "Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in the two conditions of Experiment 3.")
print(tab, type="latex", floating = TRUE, include.rownames = FALSE, comment = FALSE,
      sanitize.colnames.function = identity)

# two_alt_alphas[1,]
# three_alt_alphas[1,]
# four_alt_alphas[1,]
# five_alt_alphas[1,]
# 
# # Tuned model run data
# plotData <- allModelRunData %>%
#   mutate(study = ifelse(numAlts == 5, "Five alts", 
#                         ifelse(numAlts == 4, "Four alts",
#                                ifelse(numAlts == 3, "Two alts + generic negative ", "Two alts")))) %>%
#   gather(Experiment, cors, c(corE6, corE11)) %>%
#   mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))
# 
# tableCors <- plotData  %>%
#   select(cors, study, Experiment, alphas) %>%
#   unique() %>%
#   mutate(Experiment = ifelse(Experiment == "1b", "Pragmatic_Listener_exp1", "Pragmatic_Listener_exp2")) %>%
#   spread(Experiment, cors)
#   
# # Plot model performance table
# names(tableCors) <- c("Model", "$\\alpha$", "Two alts", "Four alts")
# tableCors <- tableCors[c(3, 4, 2, 1),]
# tab <- xtable(tableCors, caption = "Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in the two conditions of Experiment 3.")
# print(tab, type="latex", floating = TRUE, include.rownames = FALSE, comment = FALSE,
#       sanitize.colnames.function = identity)
